---
title: "dapp_testing"
author: "Minh Nguyen"
date: "10/25/2021"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)

dapp_h <- read_csv("DAPP_Data.xlsx - A.csv")

View(dapp_h)
```

Splitting the first column into two, one for date and one for time

```{r}
dapp_h <- dapp_h %>%
  separate(Time, c("Date", "Time"), " ")
```

Changing time to military time style for graphing purposes

```{r}
dapp_h <- dapp_h %>%
  separate(Time, c("Hour", "Minute", "Second"), ":")

hour_str <- as.character(dapp_h$Hour)
minute_str <- as.character(dapp_h$Minute)

dapp_h <- dapp_h %>%
  mutate(Time = gsub(" ", "", paste(hour_str, minute_str)))

dapp_h$Time <- as.numeric(dapp_h$Time)
```

Making a new variable that just shows the number of people who pass through the point, regardless of direction

```{r}
dapp_h <- dapp_h %>%
  mutate(totalpeople = Westbound + Eastbound)
```

Sums of people who pass through the points for each day

```{r}
pedestriantotals <- dapp_h %>%
  group_by(Date) %>%
  summarize(totalforday = sum(totalpeople))

pedestriantotals
```


Making a graphs for number of people who pass through H (One for Tuesday and one for Saturday)

```{r}
ggplot(filter(dapp_h, Date == "11-09-2021"), aes(x = Time, y = totalpeople)) + geom_point() + labs(title = "Location H on Saturday, September 9th", x = "Time (listed in millitary time)", y = "Total Number of People Who Passed Through", caption = "Vertical Lines Show The Granville Farmers Market Hours (8:30 AM - 12:00 PM)") + theme_classic() + geom_vline(xintercept = 830, linetype = "dashed") + geom_vline(xintercept = 1200, linetype = "dashed")

ggplot(filter(dapp_h, Date == "14-09-2021"), aes(x = Time, y = totalpeople)) + geom_point() + labs(title = "Location H on Tuesday, September 14th", x = "Time (listed in millitary time)", y = "Total Number of People Who Passed Through", caption = "Vertical Lines Show The Granville Farmers Market Hours (3:00 PM - 6:00 PM)") + theme_classic() + geom_vline(xintercept = 1500, linetype = "dashed") + geom_vline(xintercept = 1800, linetype = "dashed")
```

